Summary Tables

### 2021-11-10 summary_tables.Rmd
Add code to generate scen prop, and save it as a csv file

>>>>

```{r}

dat <- list()

dat[[city]] <- io[[city]]$trip_scen_sets %>% mutate(scenario = case_when(
  scenario == "Scenario 1" ~ "PED_SC", 
  scenario == "Scenario 2" ~ "CYC_SC",
  scenario == "Scenario 3" ~ "CAR_SC",
  scenario == "Scenario 4" ~ "MOT_SC",
  scenario == "Scenario 5" ~ "BUS_SC",
  scenario == "Baseline" ~ "Baseline")) %>% group_by(scenario, trip_mode, trip_distance_cat) %>% summarise(n = dplyr::n()) %>% mutate(city = city) %>% filter(!(trip_mode %in% "truck"))

td <- dat[[city]]

for (i in 1:nrow(td)){
    val <- td %>% filter(scenario == "Baseline", trip_mode == td$trip_mode[i] & 
                           trip_distance_cat == td$trip_distance_cat[i] &
                           city == td$city[i])

    if (nrow(val) > 0){
      td$diff[i] <- val$n - td$n[i]
      td$prop[i] <- round(td$n[i] / val$n, 2)

    }
}

dat[[city]] <- td

write_csv(bind_rows(dat), "results/multi_city/scen_prop.csv")
